---
output: rmarkdown::github_document
---

`xlsxtractr` : Extract Things From Excel (xlsx) Files

Inspired by [this SO question](http://stackoverflow.com/q/39529302/1457051).

The following functions are implemented:

- `extract_formulas`:	Extract formulas from an Excel workbook sheet
- `read_xlsx`:	Read in an Excel document for various extractions

The following data sets are included:

- `system.file("extdata/wb.xlsx", package="xlsxtractr")`: sample xlsx file

### Installation

```{r eval=FALSE}
devtools::install_git("https://gitlab.com/hrbrmstr/xlsxtractr.git")

# OR

devtools::install_github("hrbrmstr/xlsxtractr")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}
library(xlsxtractr)
library(purrr)

# current verison
packageVersion("xlsxtractr")

doc <- read_xlsx(system.file("extdata/wb.xlsx", package="xlsxtractr"))

class(doc)

print(doc)

length(doc)

extract_formulas(doc, 1)

extract_formulas(doc, 2)

extract_formulas(doc, 3) # no formula

map_df(seq_along(doc), ~extract_formulas(doc, .))
```

### Test Results

```{r echo=TRUE, message=FALSE, warning=FALSE, error=FALSE}
library(xlsxtractr)
library(testthat)

date()

test_dir("tests/")
```

